Vaccine toxins full experiment 2

### 2019-08-18 supplement/S1-structure-learning.Rmd
initiating reorg

```{r}
source("../scripts/load-data-s1.R", chdir = TRUE)
```

@@

# source("cog-model-graph-tools.R")
source("../scripts/custom-structure-learning/cog-model-main.R", chdir = TRUE)
source("../scripts/gmod_tools.R")
source("../scripts/bnTheoryBlacklist.R")
source("../scripts/custom-structure-learning/cog-model-jags-tools.R")

@@

rescale_beta <- function(x, lower, upper) {
  # rescales onto the open interval (0,1)
  # rescales over theoretical bounds of measurement, specified by "upper" and "lower"

  N <- length(x)
  res <- (x - lower) / (upper - lower)
  res <- (res * (N - 1) + .5) / N

  return(as.vector(res))
}

@@

compute_scoretables <- FALSE # uncomment to recompute scoretables
source("../scripts/custom-structure-learning/fit-cog-models.R", chdir=TRUE)

@@

scoretables <- list(
  readRDS("scoretable-unconstrained.rds"),
  readRDS("scoretable-intent_is_dv.rds"),
  readRDS("scoretable-abstract_are_parents.rds"),
  readRDS("scoretable-abstract_are_parents_intent_dv.rds"),
  readRDS("scoretable-theoryBasedHierarchy.rds")
  )

>>>>

```{r}
source("../code/load-data-s1.R", chdir = TRUE)
```

@@

source("../code/custom-structure-learning/cog-model-main.R", chdir = TRUE)
source("../code/graph-model-tools.R")
source("../code/custom-structure-learning/cog-model-jags-tools.R")
source("../code/helpers.R")

@@

@@

compute_scoretables <- FALSE # uncomment to recompute scoretables
source("../code/custom-structure-learning/fit-cog-models.R", chdir=TRUE)

@@

scoretables <- list(
  readRDS("../local/scoretable-unconstrained.rds"),
  readRDS("../local/scoretable-intent_is_dv.rds"),
  readRDS("../local/scoretable-abstract_are_parents.rds"),
  readRDS("../local/scoretable-abstract_are_parents_intent_dv.rds"),
  readRDS("../local/scoretable-theoryBasedHierarchy.rds")
  )

### 2019-08-18 supplement/s2-modeling.Rmd
initiating reorg

```{r load in existing objects, message=FALSE, warning=FALSE}
# # install missing packages
devtools::install_github("thomasp85/patchwork")
install.packages("rsample")

source("../scripts/load-data-s1.R", chdir = TRUE)
source("../scripts/gmod_tools.R")
# source("../../Scripts/virtualEvidence.R")

@@

source("../scripts/custom-structure-learning/cog-model-main.R", chdir = TRUE)
```

@@

source("../scripts/load-data-s2.R", chdir = TRUE)

>>>>

```{r load in existing objects, message=FALSE, warning=FALSE}
# # install missing packages
# devtools::install_github("thomasp85/patchwork")
# install.packages("rsample")

source("../code/load-data-s1.R", chdir = TRUE)
source("../code/graph-model-tools.R")
source("../code/helpers.R")
# source("../../Scripts/virtualEvidence.R")

@@

source("../code/custom-structure-learning/cog-model-main.R", chdir = TRUE)
```

@@

source("../code/load-data-s2.R", chdir = TRUE)

### 2019-08-18 supplement/vaccTox-full2.Rmd
initiating reorg

---
title: "Vaccine toxins full experiment"
author: Derek Powell
date: April 9, 2019
output: 
  html_notebook: 
    code_folding: hide
---

NOTE: All ps eventually saw the intervention, those in no-intervention control just saw it after they responsed to the questions. I'm not fully sure what my logic was there--equity I guess. I may have also been thinking we could ask them things about their reaction to the intervention, but we never did that. On reflection now, I think it was a poor decision. But, it doesn't seem to explain our differential dropout rate since that's mostly due to peopel dropping out at the 18% mark.

@@

```{r message=FALSE}
library(tidyverse)
library(brms)

# pre <- read_qualtrics("../data_private/vacc+tox+interv+full+-+pre_April+3,+2019_15.38.csv")
# post <- read_qualtrics("../data_private/vacc+tox+interv+full+-+post_April+5,+2019_13.59.csv")
source("../code/helpers.R")
source("../code/load-data-s3ab.R")
```

@@

```{r}
s3_scored %>%
  ggplot(aes(x=pre, fill=condition)) + 
  geom_histogram(position="dodge",alpha=.7) + 
  facet_wrap(~scale) +
  theme_bw() +
  labs(title="Histogram of pretest scores", fill = "Condition", x = "Response")

@@

s3_scored %>%
  select(workerId, condition, scale, pre) %>%
  spread(scale, pre) %>%
  select(-workerId, -condition) %>%
  cor() %>%
  reorder_cormat() %>%
  # get_lower_tri() %>%
  reshape2::melt(na.rm=TRUE) %>%
  ggplot(aes(x=Var1, y = Var2, fill = value)) +
  geom_tile(color = "white") +
  geom_tile() +
  geom_text(aes(label=round(value,2))) +
  scale_fill_distiller(type="div", palette = "RdYlBu") +
  # scale_fill_viridis_c(limit = c(-1,1)) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust=1)) +
  theme(aspect.ratio = 1) +
  theme(
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    panel.grid.major = element_blank(),
    panel.border = element_blank(),
    panel.background = element_blank(),
    axis.ticks = element_blank()
  ) +
  labs(fill="corr.")
# 
# 
# s3_scored %>%
#   select(workerId, condition, scale, pre) %>%
#   spread(scale, pre) %>%
#   select(-workerId, -condition) %>%
#   cor() %>%
#   as_tibble() %>%
#   mutate(x_scale = names(.)) %>%
#   gather(y_scale, correl, -x_scale) %>%
#   ggplot( aes(x = x_scale, y=y_scale, fill=correl)) +
#   geom_tile() +
#   scale_fill_distiller(palette="RdYlBu") +
#   theme_minimal() +
#   theme(aspect.ratio = 1) +
#   theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

@@

```{r}
s3_scored %>%
  group_by(condition, scale) %>%
  summarize(
    Mean = mean(change),
    se = sd(change)/sqrt(n())
    ) %>%
  mutate(
    ul = Mean + se,
    ll = Mean - se
  ) %>%
  ungroup() %>%
  mutate(condition = factor(condition, labels = c("Intervention","Control"))) %>%
  ggplot(aes(x=reorder(scale, Mean), color = condition, y = Mean, ymin = ll, ymax = ul)) +
  geom_errorbar(width=.1) +
  geom_point() +
  geom_hline(yintercept=0, linetype="dashed") +
  # facet_wrap(~scale) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

# s3_scored %>%
#   ggplot(aes(x=scale, color = condition, fill = condition, y = change)) +
#   geom_violin() +
#   geom_hline(yintercept=0, linetype="dashed") +
#   # facet_wrap(~scale) +
#   theme_bw() +
#   theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

```{r}
result <- s3_scored %>%
  filter(scale=="vaccTox") %>%
  group_by(condition) %>%
  summarize(
    Mean = mean(change),
    SD = sd(change)
  )

@@

__The Bad News__: The difference between conditions for vaccine intentions is driven by a decrease in the _control_ condition moreso than the increase in the intervention condition. Comparing scores just within the intervention condition against zero, the intervention is not significantly increasing intentions to vaccinate.

@@

```{r}
fit <- cbrm(
  resp ~ phase * condition + (1 | workerId),
  data = s3_scored %>%
    filter(scale == "vaccIntent") %>%
    gather(phase, resp, post, pre) %>%
    mutate(resp = rescale_beta(resp, 1, 7)),
  family = Beta(),
  prior = prior(normal(0,1), class="b"),
  chains = 2,
  cores = 2,
  iter = 2000,
  seed = 1234,
  file = "../local/s3ab-fit-vaccIntent.Rds"
)

```{r}
t.test(s3_scored %>% filter(scale=="vaccIntent", condition=="intervention") %>% .$change)
```

In contrast, the difference in the control condition for vaccine intentions is really quite huge. A one-sample t-test remains significant after correcting for multiple comparisons (bonferroni adjusted $\alpha$ = .0036).

```{r}
t.test(s3_scored %>% filter(scale=="vaccIntent", condition=="noInterv") %>% .$change)
```

So unfortunately something really is amiss with these vaccine intentions responses. There are also some suspicious changes in a handful of other beliefs: vaccine toxicity, holistic balance, naturalism, and infant immune system weakness, but using a one-sample t-test, but none of those changes are significantly different from zero by conventional standards, even without correcting for multiple comaprisons.

@@

summary(
  lm(post ~ pre + condition, data = s3_scored %>% filter(scale=="vaccDanger"))
)

s3_scored %>%
  filter(scale=="vaccIntent") %>%
  ggplot(aes(x=pre, y = post, color=condition)) +
  geom_jitter() + 
  theme_bw() +
  theme(aspect.ratio=1)
```

@@

```{r}
pretest_scores <- s3_scored %>%
  filter(scale=="vaccIntent") %>%
  group_by(condition) %>%
  summarize(
    pre_mean = mean(pre),
    pre_sd = sd(pre),
    )

t.test(pre ~ condition, 
       data = s3_scored %>% filter(scale=="vaccIntent")
       )

s3_scored %>%
  filter(scale=="vaccIntent") %>%
  group_by(condition) %>%
  summarize(
    pre_mean = mean(pre),
    pre_se = sd(pre)/sqrt(n()),
    ) %>%
  mutate(
    ll = pre_mean - pre_se,
    ul = pre_mean + pre_se
  ) %>%
  ggplot(aes(x=condition, y=pre_mean, ymin=ll, ymax=ul)) +
  geom_pointrange() +
  theme_bw()
```

@@

```{r}
s3_scored %>%
  filter(scale=="vaccIntent") %>%
  filter(!is.na(parent)) %>%
  group_by(parent, condition) %>%
  summarize(mean_change = mean(change),
            se = sd(change)/sqrt(n()),
            N = n()
            ) %>%
  ungroup() %>%
  mutate(
    ll = mean_change - se,
    ul = mean_change + se,
    parent=factor(parent, labels=c("non-parents","parents"))
    ) %>%
  ggplot(aes(x=parent, y = mean_change, ymin = ll, ymax=ul, color=condition)) +
  geom_pointrange(position=position_dodge(width=.25)) +
  theme_bw()
```

@@

```{r}
# x <- t.test(s3_scored %>% filter(scale=="vaccIntent", condition=="noInterv") %>% .$change)

get_t_stat <- function(scale){
  data <- s3_scored %>% filter(scale==!!scale, condition=="noInterv")

@@

obs_F <- tibble(
  scale = unique(s3_scored$scale),
  t = map_dbl(scale, get_t_stat),
  F_stat = t^2
  ) %>%
  summarize(F_mean = mean(F_stat))

obs_F_noVacc <- tibble(
  scale = unique(s3_scored$scale),
  t = map_dbl(scale, get_t_stat),
  F_stat = t^2
  ) %>%
  filter(scale!="vaccIntent") %>% # comment
  summarize(F_mean = mean(F_stat))

tibble(x = rep(14,5000)) %>%
  mutate(F_mean = map_dbl(x, function(x){ mean(rt(x, 493)^2) }) ) %>%
  mutate(greater = ifelse(F_mean > obs_F$F_mean, 1, 0)) %>%
  summarize(p = mean(greater))

tibble(x = rep(13,5000)) %>%
  mutate(F_mean = map_dbl(x, function(x){ mean(rt(x, 493)^2) }) ) %>%
  mutate(greater = ifelse(F_mean > obs_F_noVacc$F_mean, 1, 0)) %>%
  summarize(p_no_vaccIntent = mean(greater))
```

Doing a bootstrap, things are overall more extreme than expected under the null across the 14 beliefs. If we remove the vaccIntent scale from consideration however, then things are no more extreme than expected.

Unfortunately that really just adds to the mystery--if there were systematic variations it would feel safe to conclude that "something happened" that affected resposnes in the control condition, suggesting these results are generally suspect. But it seems isolated to the vaccIntent scale. Nevertheless, it's problematic for our purposes.

@@

d_vacctox <- s3_scored %>%
  select(-change) %>%
  gather(phase, mean, pre,post) %>%
  mutate(mean = mean-4) %>%
  ungroup()

@@

saveRDS(object = pred_changes, file = "pred_changes.Rds")
```

@@

pred_changes <- readRDS("pred_changes.Rds")

preds_obs <- s3_scored %>%
  filter(condition == "intervention") %>%
  group_by(scale) %>%
  mutate(
    pre = rescale_beta((pre - 4), -3, 3),
    post = rescale_beta((post - 4), -3, 3)
  ) %>%
  mutate(change = post - pre) %>%
  summarize(
    Mean = mean(change),
    se = sd(change) / sqrt(n())
  ) %>%
  mutate(
    ul = Mean + se,
    ll = Mean - se
  ) %>%
  left_join(pred_changes %>% rename(pred_mean = Mean), by = "scale")

@@

preds_obs2 <- s3_scored %>%
  filter(condition == "intervention") %>%
  group_by(scale) %>%
  mutate(
    pre = rescale_beta((pre - 4), -3, 3),
    post = rescale_beta((post - 4), -3, 3)
  ) %>%
  mutate(change = post - pre) %>%
  summarize(
    Mean = mean(change),
    se = sd(change) / sqrt(n())
  ) %>%
  mutate(
    ul = Mean + se,
    ll = Mean - se
  ) %>%
  left_join(pred_changes2 %>% rename(pred_mean = Mean), by = "scale")

@@

s3_scored %>%
  filter(scale=="vaccTox") %>%
  ggplot(aes(x=condition, y = change)) +
  geom_boxplot(width=.25) +
  theme_bw()

s3_scored %>%
  filter(scale=="vaccTox") %>%
  ggplot(aes(x=condition, y = change)) +
  stat_summary(fun.y = mean, geom = "point", size=3) + 
  stat_summary(fun.data = mean_se, geom = "errorbar", width=.1) +
  theme_bw() +
  labs(x="Condition", y = "Mean Change Score")
```

@@

preds_obs <- s3_scored %>%
    group_by(condition, scale) %>%
  summarize(
    Mean = mean(change),
    se = sd(change)/sqrt(n())
    ) %>%
  mutate(
    ul = Mean + se,
    ll = Mean - se
  ) %>%
  filter(condition=="intervention") %>%
  left_join(preds, by ="scale")

cors <- s3_scored %>%
  ungroup() %>%
  select(workerId, scale, pre) %>%
  spread(scale, pre) %>%
  select(-workerId) %>%
  cor() %>%
  .["vaccTox",] %>%
  tibble(pred_cor = ., scale=names(.))

@@

```{r}
preds_obs2 <- s3_scored %>%
    group_by(condition, scale) %>%
  summarize(
    Mean = mean(change)
    # se = sd(change)/sqrt(n())
    ) %>%
  spread(condition, Mean) %>%
  mutate(difference = intervention - noInterv) %>%
  left_join(cors, by ="scale") %>%
  mutate(pred_cor = pred_cor/sd(.$pred_cor)*-1,
         difference = difference/sd(.$difference),
         intervention = intervention/sd(.$intervention)
         )

@@

preds_obs <- s3_scored %>%
  filter(condition == "noInterv") %>%
  group_by(scale) %>%
  mutate(
    pre = rescale_beta((pre - 4), -3, 3),
    post = rescale_beta((post - 4), -3, 3)
  ) %>%
  mutate(change = post - pre) %>%
  summarize(
    Mean = mean(change),
    se = sd(change) / sqrt(n())
  ) %>%
  mutate(
    ul = Mean + se,
    ll = Mean - se
  ) %>%
  left_join(pred_changes %>% rename(pred_mean = Mean), by = "scale")

@@

```{r}
pre_control <- summary(lm(
  vaccIntent ~ vaccDanger + vaccEff + vaccStrain + vaccTox + diseaseRare + diseaseSevere + diseaseRare + medSkept + hb + nat + infantImmLimCap + infantImmWeak,
  data = s3_scored %>% 
    gather(phase, mean, pre, post) %>% 
    select(-parent, -change) %>%
    spread(scale, mean) %>% 
    filter(phase=="pre", condition=="noInterv")
))

post_control <- summary(lm(
  vaccIntent ~ vaccDanger + vaccEff + vaccStrain + vaccTox + diseaseRare + diseaseSevere + diseaseRare + medSkept + hb + nat + infantImmLimCap + infantImmWeak,
  data = s3_scored %>% 
    gather(phase, mean, pre, post) %>% 
    select(-parent, -change) %>%
    spread(scale, mean) %>% 
    filter(phase=="post", condition=="noInterv")
))

pre_interv <- summary(lm(
  vaccIntent ~ vaccDanger + vaccEff + vaccStrain + vaccTox + diseaseRare + diseaseSevere + diseaseRare + medSkept + hb + nat + infantImmLimCap + infantImmWeak,
  data = s3_scored %>% 
    gather(phase, mean, pre, post) %>% 
    select(-parent, -change) %>%
    spread(scale, mean) %>% 
    filter(phase=="pre", condition=="intervention")
))

post_interv <- summary(lm(
  vaccIntent ~ vaccDanger + vaccEff + vaccStrain + vaccTox + diseaseRare + diseaseSevere + diseaseRare + medSkept + hb + nat + infantImmLimCap + infantImmWeak,
  data = s3_scored %>% 
    gather(phase, mean, pre, post) %>% 
    select(-parent, -change) %>%
    spread(scale, mean) %>% 
    filter(phase=="post", condition=="intervention")
))

>>>>

---
title: "Vaccine toxins full experiment 2"
author: Derek Powell
date: April 9, 2019
output: 
  html_notebook: 
    code_folding: hide
---

This is the second attempt at testing this intervention, hoping that we won't see changes in control condition this time.

@@

```{r message=FALSE}
# !diagnostics off
library(tidyverse)
```

```{r message=FALSE}
read_qualtrics <- function(fname){
    # load raw qualtrics data
  header <- colnames(read.csv(fname, header = TRUE))
  df <- read.csv(fname, skip = 3, header = FALSE, col.names = header)

  # do some preliminary tidying
  df <- df %>%
    as_tibble()

  return(df)
}

rcor <- function(x,y=NULL){
  r <- cor(x,y)
  return( round(r,3) )
}

pre <- read_qualtrics("../data_private/vacc+tox+interv+full2+-+pre_June+6,+2019_09.35.csv")
post <- read_qualtrics("../data_private/vacc+tox+interv+full2+-+post_June+7,+2019_18.00.csv")
```

```{r warning=FALSE}

df_pre <- pre %>%
  distinct(workerId, .keep_all = TRUE) %>%
  filter(Progress==100, check_3==3, check_5==5) %>%
  mutate(parent = recode(parent, `23`=1, `24`=0)) %>%
  select(workerId, matches(".*(_[0-9])"), -check_3, -check_5, parent) %>%
  gather(item, resp, -workerId, -parent) %>%
  mutate(item = paste0("pre_",item)) %>%
  spread(item, resp)

df_post <- post %>%
  filter(Progress==100, check_3==3, check_5==5) %>%
  select(workerId, matches(".*(_[0-9])"), -check_3, -check_5,
         condition, interv_t_Page.Submit) %>%
  rename(read_time = interv_t_Page.Submit) %>%
  gather(item, resp, -workerId, -condition, -read_time) %>%
  mutate(item = paste0("post_",item)) %>%
  spread(item, resp)

df <- left_join(filter(df_pre, workerId %in% df_post$workerId), df_post, by="workerId") %>%
  mutate_at(vars(matches(".*(_[0-9]*r)")), funs(8 - .)) %>% # reverse code
  gather(item, resp, matches(".*(_[0-9])")) %>%
  mutate(phase = ifelse(grepl("pre_",item),"pre","post")) %>%
  mutate(
    item = gsub("pre_","",item),
    item = gsub("post_","",item)
    ) %>%
  mutate(scale = gsub("(_([0-9])+(r)*)","",item))

df_scored <- df %>%
  group_by(workerId, condition, scale, phase, parent) %>%
  summarize(mean_resp = mean(resp)) %>%
  spread(phase, mean_resp) %>%
  mutate(change = post - pre) %>%
  ungroup()

@@

```{r}
df_scored %>%
  ggplot(aes(x=pre, fill=condition)) + 
  geom_histogram(position="dodge",alpha=.7) + 
  facet_wrap(~scale) +
  theme_bw() +
  labs(title="Histogram of pretest scores", fill = "Condition", x = "Response")

@@

df_scored %>%
  select(workerId, condition, scale, pre) %>%
  spread(scale, pre) %>%
  select(-workerId, -condition) %>%
  cor() %>%
  reorder_cormat() %>%
  # get_lower_tri() %>%
  reshape2::melt(na.rm=TRUE) %>%
  ggplot(aes(x=Var1, y = Var2, fill = value)) +
  geom_tile(color = "white") +
  geom_tile() +
  geom_text(aes(label=round(value,2))) +
  scale_fill_distiller(type="div", palette = "RdYlBu") +
  # scale_fill_viridis_c(limit = c(-1,1)) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust=1)) +
  theme(aspect.ratio = 1) +
  theme(
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    panel.grid.major = element_blank(),
    panel.border = element_blank(),
    panel.background = element_blank(),
    axis.ticks = element_blank()
  ) +
  labs(fill="corr.")
# 
# 
# df_scored %>%
#   select(workerId, condition, scale, pre) %>%
#   spread(scale, pre) %>%
#   select(-workerId, -condition) %>%
#   cor() %>%
#   as_tibble() %>%
#   mutate(x_scale = names(.)) %>%
#   gather(y_scale, correl, -x_scale) %>%
#   ggplot( aes(x = x_scale, y=y_scale, fill=correl)) +
#   geom_tile() +
#   scale_fill_distiller(palette="RdYlBu") +
#   theme_minimal() +
#   theme(aspect.ratio = 1) +
#   theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

@@

```{r}
df_scored %>%
  group_by(condition, scale) %>%
  summarize(
    Mean = mean(change),
    se = sd(change)/sqrt(n())
    ) %>%
  mutate(
    ul = Mean + se,
    ll = Mean - se
  ) %>%
  ungroup() %>%
  mutate(condition = factor(condition, labels = c("Intervention","Control"))) %>%
  ggplot(aes(x=reorder(scale, Mean), color = condition, y = Mean, ymin = ll, ymax = ul)) +
  geom_errorbar(width=.1) +
  geom_point() +
  geom_hline(yintercept=0, linetype="dashed") +
  # facet_wrap(~scale) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

# df_scored %>%
#   ggplot(aes(x=scale, color = condition, fill = condition, y = change)) +
#   geom_violin() +
#   geom_hline(yintercept=0, linetype="dashed") +
#   # facet_wrap(~scale) +
#   theme_bw() +
#   theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

```{r}
result <- df_scored %>%
  filter(scale=="vaccTox") %>%
  group_by(condition) %>%
  summarize(
    Mean = mean(change),
    SD = sd(change)
  )

@@

__The Bad News__: The difference between conditions for vaccine intentions is PARTIALLY driven by a decrease in the _control_ condition moreso than the increase in the intervention condition. Comparing scores just within the intervention condition against zero, the intervention is not significantly increasing intentions to vaccinate.

@@

```{r}
t.test(df_scored %>% filter(scale=="vaccIntent", condition=="intervention") %>% .$change)
```

This time, the control condition isn't significantly different from zero either.

```{r}
t.test(df_scored %>% filter(scale=="vaccIntent", condition=="noInterv") %>% .$change)
```

So unfortunately we have essentially the same problem once again with the vaccine intentions responses.

And this time there are now a bunch of additional (!) suspicious changes in a handful of other beliefs, notably holistic balance and medical skepticism.

@@

summary(
  lm(post ~ pre + condition, data = df_scored %>% filter(scale=="vaccIntent"))
)

df_scored %>%
  filter(scale=="vaccIntent") %>%
  ggplot(aes(x=pre, y = post, color=condition)) +
  geom_jitter() + 
  theme_bw() +
  theme(aspect.ratio=1)
```

@@

```{r}
pretest_scores <- df_scored %>%
  filter(scale=="vaccIntent") %>%
  group_by(condition) %>%
  summarize(
    pre_mean = mean(pre),
    pre_sd = sd(pre),
    )

t.test(pre ~ condition, 
       data = df_scored %>% filter(scale=="vaccIntent")
       )

df_scored %>%
  filter(scale=="vaccIntent") %>%
  group_by(condition) %>%
  summarize(
    pre_mean = mean(pre),
    pre_se = sd(pre)/sqrt(n()),
    ) %>%
  mutate(
    ll = pre_mean - pre_se,
    ul = pre_mean + pre_se
  ) %>%
  ggplot(aes(x=condition, y=pre_mean, ymin=ll, ymax=ul)) +
  geom_pointrange() +
  theme_bw()
```

@@

```{r}
df_scored %>%
  filter(scale=="vaccIntent") %>%
  filter(!is.na(parent)) %>%
  group_by(parent, condition) %>%
  summarize(mean_change = mean(change),
            se = sd(change)/sqrt(n()),
            N = n()
            ) %>%
  ungroup() %>%
  mutate(
    ll = mean_change - se,
    ul = mean_change + se,
    parent=factor(parent, labels=c("non-parents","parents"))
    ) %>%
  ggplot(aes(x=parent, y = mean_change, ymin = ll, ymax=ul, color=condition)) +
  geom_pointrange(position=position_dodge(width=.25)) +
  theme_bw()
```

@@

```{r}
# x <- t.test(df_scored %>% filter(scale=="vaccIntent", condition=="noInterv") %>% .$change)

get_t_stat <- function(scale){
  data <- df_scored %>% filter(scale==!!scale, condition=="noInterv")

@@

obs_F <- tibble(
  scale = unique(df_scored$scale),
  t = map_dbl(scale, get_t_stat),
  F_stat = t^2
  ) %>%
  summarize(F_mean = mean(F_stat))

obs_F_noVacc <- tibble(
  scale = unique(df_scored$scale),
  t = map_dbl(scale, get_t_stat),
  F_stat = t^2
  ) %>%
  filter(scale!="vaccIntent") %>% # comment
  summarize(F_mean = mean(F_stat))

tibble(x = rep(14,5000)) %>%
  mutate(F_mean = map_dbl(x, function(x){ mean(rt(x, 250)^2) }) ) %>%
  mutate(greater = ifelse(F_mean > obs_F$F_mean, 1, 0)) %>%
  summarize(p = mean(greater))

tibble(x = rep(13,5000)) %>%
  mutate(F_mean = map_dbl(x, function(x){ mean(rt(x, 250)^2) }) ) %>%
  mutate(greater = ifelse(F_mean > obs_F_noVacc$F_mean, 1, 0)) %>%
  summarize(p_no_vaccIntent = mean(greater))
```

Doing a bootstrap, things are overall more extreme than expected under the null across the 14 beliefs. This is also true if we remove the vaccIntent scale from consideration. So it seems that it was not safe to run this study again 😢.

@@

d_vacctox <- df_scored %>%
  select(-change) %>%
  gather(phase, mean, pre,post) %>%
  mutate(mean = mean-4) %>%
  ungroup()

@@

# saveRDS(object = pred_changes, file = "pred_changes.Rds")
```

@@

# pred_changes <- readRDS("pred_changes.Rds")

preds_obs <- df_scored %>%
  filter(condition == "intervention") %>%
  group_by(scale) %>%
  mutate(
    pre = rescale_beta((pre - 4), -3, 3),
    post = rescale_beta((post - 4), -3, 3)
  ) %>%
  mutate(change = post - pre) %>%
  summarize(
    Mean = mean(change),
    se = sd(change) / sqrt(n())
  ) %>%
  mutate(
    ul = Mean + se,
    ll = Mean - se
  ) %>%
  left_join(pred_changes %>% rename(pred_mean = Mean), by = "scale")

@@

preds_obs2 <- df_scored %>%
  filter(condition == "intervention") %>%
  group_by(scale) %>%
  mutate(
    pre = rescale_beta((pre - 4), -3, 3),
    post = rescale_beta((post - 4), -3, 3)
  ) %>%
  mutate(change = post - pre) %>%
  summarize(
    Mean = mean(change),
    se = sd(change) / sqrt(n())
  ) %>%
  mutate(
    ul = Mean + se,
    ll = Mean - se
  ) %>%
  left_join(pred_changes2 %>% rename(pred_mean = Mean), by = "scale")

@@

df_scored %>%
  filter(scale=="vaccTox") %>%
  ggplot(aes(x=condition, y = change)) +
  geom_boxplot(width=.25) +
  theme_bw()

df_scored %>%
  filter(scale=="vaccTox") %>%
  ggplot(aes(x=condition, y = change)) +
  stat_summary(fun.y = mean, geom = "point", size=3) + 
  stat_summary(fun.data = mean_se, geom = "errorbar", width=.1) +
  theme_bw() +
  labs(x="Condition", y = "Mean Change Score")
```

@@

preds_obs <- df_scored %>%
    group_by(condition, scale) %>%
  summarize(
    Mean = mean(change),
    se = sd(change)/sqrt(n())
    ) %>%
  mutate(
    ul = Mean + se,
    ll = Mean - se
  ) %>%
  filter(condition=="intervention") %>%
  left_join(preds, by ="scale")

cors <- df_scored %>%
  ungroup() %>%
  select(workerId, scale, pre) %>%
  spread(scale, pre) %>%
  select(-workerId) %>%
  cor() %>%
  .["vaccTox",] %>%
  tibble(pred_cor = ., scale=names(.))

@@

```{r}
preds_obs2 <- df_scored %>%
    group_by(condition, scale) %>%
  summarize(
    Mean = mean(change)
    # se = sd(change)/sqrt(n())
    ) %>%
  spread(condition, Mean) %>%
  mutate(difference = intervention - noInterv) %>%
  left_join(cors, by ="scale") %>%
  mutate(pred_cor = pred_cor/sd(.$pred_cor)*-1,
         difference = difference/sd(.$difference),
         intervention = intervention/sd(.$intervention)
         )

@@

preds_obs <- df_scored %>%
  filter(condition == "noInterv") %>%
  group_by(scale) %>%
  mutate(
    pre = rescale_beta((pre - 4), -3, 3),
    post = rescale_beta((post - 4), -3, 3)
  ) %>%
  mutate(change = post - pre) %>%
  summarize(
    Mean = mean(change),
    se = sd(change) / sqrt(n())
  ) %>%
  mutate(
    ul = Mean + se,
    ll = Mean - se
  ) %>%
  left_join(pred_changes %>% rename(pred_mean = Mean), by = "scale")

@@

```{r}
pre_control <- summary(lm(
  vaccIntent ~ vaccDanger + vaccEff + vaccStrain + vaccTox + diseaseRare + diseaseSevere + diseaseRare + medSkept + hb + nat + infantImmLimCap + infantImmWeak,
  data = df_scored %>% 
    gather(phase, mean, pre, post) %>% 
    select(-parent, -change) %>%
    spread(scale, mean) %>% 
    filter(phase=="pre", condition=="noInterv")
))

post_control <- summary(lm(
  vaccIntent ~ vaccDanger + vaccEff + vaccStrain + vaccTox + diseaseRare + diseaseSevere + diseaseRare + medSkept + hb + nat + infantImmLimCap + infantImmWeak,
  data = df_scored %>% 
    gather(phase, mean, pre, post) %>% 
    select(-parent, -change) %>%
    spread(scale, mean) %>% 
    filter(phase=="post", condition=="noInterv")
))

pre_interv <- summary(lm(
  vaccIntent ~ vaccDanger + vaccEff + vaccStrain + vaccTox + diseaseRare + diseaseSevere + diseaseRare + medSkept + hb + nat + infantImmLimCap + infantImmWeak,
  data = df_scored %>% 
    gather(phase, mean, pre, post) %>% 
    select(-parent, -change) %>%
    spread(scale, mean) %>% 
    filter(phase=="pre", condition=="intervention")
))

post_interv <- summary(lm(
  vaccIntent ~ vaccDanger + vaccEff + vaccStrain + vaccTox + diseaseRare + diseaseSevere + diseaseRare + medSkept + hb + nat + infantImmLimCap + infantImmWeak,
  data = df_scored %>% 
    gather(phase, mean, pre, post) %>% 
    select(-parent, -change) %>%
    spread(scale, mean) %>% 
    filter(phase=="post", condition=="intervention")
))
